\documentclass[conference]{IEEEtran}
\usepackage{epsfig,endnotes}
\usepackage[hyphens]{url}
\usepackage{color}
\usepackage{comment}
\usepackage{float}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{lipsum}
\usepackage{pifont} %used for tickmark and crosses.
\usepackage{array}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage[normalem]{ulem}
\usepackage{xspace}
\usepackage{fancyvrb}
\usepackage{fixltx2e}

\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand{\sysname}{Sensibility Testbed\xspace}

\newcommand{\sensorname}{Sensorium\xspace}
\newcommand{\blurname}{BlurSense\xspace}

%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}

\hypersetup{%
  pdftitle = {TBD},
  pdfkeywords = {},
  pdfauthor = {TBD},
  bookmarksnumbered,
  bookmarksopen=true,
  colorlinks=true,
  urlcolor=[rgb]{.35,0,0},
  linkcolor=[rgb]{.35,0,0},
  citecolor=[rgb]{.35,0,0},
  pdfstartview={FitH},
}

\newcommand{\eat}[1]{}
\newcommand{\rmv}[1]{ #1}

\newif\ifrev
% comment out the following line after the revision is done
\revtrue
\ifrev
  \newcommand{\cappos}[1]{{\color{red} [Justin: #1]}}
  \newcommand{\yanyan}[1]{{\color{blue} [Yanyan: #1]}}
\else
  \newcommand{\cappos}[1]{}
  \newcommand{\yanyan}[1]{}
\fi

\begin{document}

\title{\blurname: Dynamic Fine-Grained Access Control to Protect 
Smartphone Users’ Privacy}

\author{\IEEEauthorblockN{Homer}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{Bart}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: bart@thesimpsons.com}}

\maketitle


\begin{abstract}
For many people, smartphones serve as a technical interface to the modern world.
Access to devices at the network edge, such as tablets and smartphones, is
immensely valuable to researchers. More importantly, these smart devices also
have embedded on-board sensors, such as accelerometer, gyroscope, GPS, and
camera, which enable \yanyan{find a better word than ``enable''.} the
development of innovative mobile applications. 

This work builds \blurname, a tool that provides secure and customizable access
to a large number of sensors on smartphones, tablets, and similar end user
devices. The current access control to the smartphone resources, such as sensor
data, is static and coarse-grained. \blurname is a dynamic, fine-grained access
control mechanism, acting as a defensive line that allows to define and add
privacy filters from user space. As a results, any user can can securely expose
sensor data to the outside world, and any researchers can securely share the
privacy filters with other researchers to improve the capabilities of each
other's experiment.
\yanyan{need work on the last sentence...doesn't sound right.}
\end{abstract}

\IEEEpeerreviewmaketitle

\input{intro}
\input{architecture}
\input{design}

\section{Conclusion}


% \section*{Acknowledgment}


\bibliographystyle{IEEEtran}
\bibliography{bibdata}

\end{document}